### 2021-05-14 docs/manuscript/PLOS-MSc-Thesis.tex
Add description of Fig S4 and cite it in text

In order to classify each topology by its subgraph composition, we first created
a matrix  $T = (t_{ij})$ with 714 rows corresponding to each different topology
and 17 columns corresponding to different subgraphs. Each element $t_{ij}$ of
the matrix was 1 if the \emph{j}-th subgraph was present in the \emph{i}-th
topology or 0 if the subgraph was not present.\\

@@

\paragraph*{S4 Fig.}
\label{S4_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}

>>>>

In order to classify each topology by its subgraph composition, we first created
a matrix  $T = (t_{ij})$ with 714 rows corresponding to each different topology
and 17 columns corresponding to subgraphs shown in \nameref{S4_Fig}.
Each element $t_{ij}$ of
the matrix was 1 if the \emph{j}-th subgraph was present in the \emph{i}-th
topology or 0 if the subgraph was not present.\\

@@

\paragraph*{S4 Fig.}
\label{S4_Fig}
{\bf Relevant subgraphs present in the set of GRNs.}
These are subgraphs that have been reported in previous studies as networks
involved in morphogenesis and development \cite{Cotterell2010, Schaerli2014,
Schaerli2018}. These were used to calculate the subgraph profile and the results
reported in \nameref{S1_Table}.
